\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-28 paper.tex
caption for fig 2

\caption{\label{fig-scurve-true-sc}Three views of the true model in
projections from \(7\text{-}D\), for the S-curve data. The model closely
fits the shape. (The \textbf{langevitour} software is used to view the
data with a tour, and the full video is available at
\url{https://youtu.be/I5GL23vLiw0}).}

>>>>

\caption{\label{fig-scurve-true-sc}Three views of the true model (grey
points and lines) in \(2\text{-}D\) projections from \(7\text{-}D\), for
the S-curve data (purple points). The data is spread along the S shape,
and does not vary much from this curve. (The \textbf{langevitour}
software is used to view the data with a tour, and the full video is
available at \url{https://youtu.be/I5GL23vLiw0}).}
